\documentclass[margin,10pt]{resume}
\usepackage{hyperref}

\begin{document}
\begin{resume}

\vspace{15mm}

\section{\mysidestyle Scholastic\\Achievements}

\begin{list2}
\item Selected for the \textbf{INPHO} (Physics), \textbf{INCHO} (Chemistry),\textbf{INAO} (Astronomy), \textbf{ INMO} (Mathematics) National Top 1\% \hfill \emph{2010}
\item \textbf{All India Rank 589} in IITJEE (Top 0.01\% ) \hfill \emph{2011}
\item Achieved an \textbf{All India Rank 36} in ISAT 2011 conducted by Indian Institute of Space Technology (Top 0.03\% )
\hfill \emph{2011}
\item Pursuing a \emph{Minor} in Electrical Engineering.
\end{list2}
\section{\mysidestyle Research\\And\\Internships }
\textbf{Keyword Detection in Continuous Speech} \\
    \textsl{Guide : Prof. Ganesh Ramakrishna} \hfill \emph{Summer 2013} \\
     Looked into possible usage of \emph{Markov Matrices} for keyword detection in recorded voice messages and the subsequent categorization of the messages according to the keyword detected.

\textbf{Web Developer} at \emph{CourseBrew} \hfill \emph{Autumn 2013} \\
Developed a prototype of an online education website. Extensively used \emph{DHTMLx} and \emph{Javascript} to create the discussion forum and \emph{dynamic layouts} for the web application.

\section{\mysidestyle Academic\\Projects}

\textbf{Tum Tum Tracker} \hfill Bus Tracking System \hfill
    \url{http://www.tttracker.in} \\
 Developed the web app using \emph{Google Maps API v3} and asynchronously fetched bus positions and updated them realtime  on the application.

\textbf{Handwriting Calculator} \hfill
    \textsl{Guide : Prof. Varsha Apte} \hfill \emph{Autumn 2012}\\
 \emph{A handwriting based calculator} designed using \textbf{Supervised Machine Learning} based on \emph{feature extraction} and DTW to find optimal character match.

\textbf{GIS Contour Plotting}
  \hfill \textsl{Guide : Prof. Milind Sohoni} \hfill \emph{Summer 2012}\\
Plotting \textbf{elevation contours} using sample data point from \emph{Google Maps API}.Generated \emph{KML} files and overlaid them on \emph{Google Earth} using \emph{python} scripts.

\textbf{8-Point FFT on FPGA} \hfill \textsl{Guide: Prof. Ashwin Gumasthe} \hfill \emph{Spring 2013} \\
 Designed, implemented \emph{Fast Fourier Transform} on a Field Programmable Gate Array 

\section{\mysidestyle Positions of\\Responsibility } 
\textbf{Manager} of \emph{The Web and Coding Club} \hfill \emph{2013-2014}\\
WnCC is one of the biggest clubs of IIT Bombay which supports coding and related activities in the institute. Responsibility as a manager includes
\begin{list2}
\item Conducting workshops, sessions and competitions to improve coding culture among the students and to introduce the community to latest developments in technology, acting as a bridge between the academia and the industry. 
\item Organized major collaborative events in the past which include Yahoo HackU!, Google Appathon (GDG Mumbai), Firefox OS Hackathon (Mozilla India). 
\end{list2}\textbf{GSA} Google Student Ambassador of IIT Bombay \hfill \emph{2013-2014} \\
\textbf{Convener} of Maths and Physics Club \hfill \emph{2012-2013} 

\section{\mysidestyle Extra \\ Curricular \\ Activities }
\begin{list2}
\item Active contributor to \textbf{Open Source Projects} with contributions for \emph{Firefox QA} and \emph{Firefox for Android}.
\item Created an automatic song tagging application in \emph{Windows 8 Appfest} held in Bengaluru and was the \emph{Runnerup} of the Institute Hackathon conducted by WnCC.
\end{list2}
\section{\mysidestyle Key Courses\\Undertaken}
\textbf{Core:} 
Abstractions and Paradigms in Programming, Computer Architecture*, Database Systems* ,Design and Analysis of Algorithms, Networks*, Automata Theory and Logic, Discrete Structures, Software Systems, Logic Design\\
\textbf{Breadth:} 
Calculus,Economics,Numerical Analysis,Analog Electronics*,Data Analysis and Interpretation,Signals and Systems,Controls and Communications,Linear Algebra and Differential Equations,Introduction to Electric and Electronics Circuits \\
\textbf{Note:} The * marked courses will be completed by November 2013.

\end{resume}
\end{document}
