\documentclass[margin,11pt]{resume}
\usepackage{hyperref}

\begin{document}
\begin{resume}

\vspace{25mm}

\section{\mysidestyle Scholastic\\Achievements}

\begin{list2}
\item Secured $12^{th}$ position in \textbf{Regional Mathematics Olympiad} conducted by the \emph{Dept. of Mathematics University of Rajasthan} \hfill \emph{2009}
\item Awarded \textbf{AIR 12} for AMTI's \emph{Association of Mathematics Teacher of India} NMTC \emph{National Maths Talent Contest} \hfill \emph{2009}
\item Selected for the following national olympiads:
\begin{list2}
\item \textbf{INPHO} \emph{Physics} National Top 1 \% \hfill \emph{2010}
\item \textbf{INPHO} \emph{Chemistry} National Top 1 \% \hfill \emph{2010}
\item \textbf{INPHO} \emph{Astronomy} National Top 1 \% \hfill \emph{2007,2010}
\item \textbf{INMO} \emph{Mathematics} National Top 1 \% \hfill \emph{2009,2010}
\end{list2}
\vspace{2mm}
\item \textbf{All India Rank 589} in IITJEE 2011 (Top 0.01\% )
\item Achieved an \textbf{All India Rank 36} in ISAT 2011 conducted by Indian Institute of Space Technology (Top 0.03\% )
\item Pursuing \emph{minor} in Electrical Engineering.
\end{list2}\vspace{0.25mm}
\section{\mysidestyle Research\\And\\Internships }
\textbf{Keyword Detection in Continuous Speech} \\
    \textsl{Guide : Prof. Ganesh Ramakrishna} \hfill \emph{Summer 2013}
\begin{list2}
\item Developed a \emph{Voice based Application} in \emph{Spring MVC} framework for developing a voice based discussion forum . 
\item Looked into possible usage of \emph{Markov Matrices} for keyword detection in recorded voice messages and the subsequent categorization of the messages according to the keyword detected.
\end{list2}

\textbf{Web Developer} at \emph{CourseBrew} \hfill \emph{Autumn 2013} \\
Developed a prototype of an online education website. Extensively used \emph{DHTMLx} and \emph{Javascript} to create the discussion forum and \emph{dynamic layouts} for various sections of the web application.

\section{\mysidestyle Positions of\\Responsibility } 


\textbf{Manager} of \emph{The Web and Coding Club} \hfill \emph{2013-2014}\\
WnCC is one of the biggest clubs of IIT Bombay which supports coding and related activities in the institute. Responsibility as a manager includes
\begin{list2}
\item Conducting workshops, sessions and competitions to improve coding culture among the students and to introduce the community to latest developments in technology, acting as a bridge between the academia and the industry. 
\item Creating awareness about Open Source and encouraging students towards contribution to the same. 
\item Organized major collaborative events in the past which include Yahoo HackU!, Google Appathon (GDG Mumbai), Firefox OS Hackathon (Mozilla India). 
\item Managing student projects and open source initiatives of the club. 
\end{list2}
\textbf{GSA} Google Student Ambassador of IIT Bombay \hfill \emph{2013-2014} \\
\emph{Working as a part of the global GSA community in improving the internet literacy}
\textbf{Convener} of Maths and Physics Club \hfill \emph{2012-2013} \\
\emph{Part of Students Technical Activity Body (STAB), monitoring and mentoring Technical Activities all over the institute}

\vspace{20mm}
\section{\mysidestyle Academic\\Projects}

\textbf{Tum Tum Tracker} \hfill Bus Tracking System \hfill
    \url{http://www.tttracker.in}
\begin{list2}
\item Designing and developing an indigenous Bus Tracking System under the purview of Technovation IITB.
\item Developed the \emph{API Mode} for XBEE to wirelessly transmit and receive data in a mesh network using \emph{Zigbee protocol}.
\item Developed the web app using \emph{Google Maps API v3} and asynchronously fetched bus positions and updated them realtime  on the application.
\end{list2}

\textbf{Handwriting Calculator} \hfill
    \textsl{Guide : Prof. Varsha Apte} \hfill \emph{Autumn 2012}
\begin{list2}
\item \emph{A handwriting based calculator} which identifies and evaluates mathematical expressions written via hand held input.
\item Implemented \textbf{Supervised Machine Learning} based on \emph{feature extraction}. 
\item Used Dynamic Time Warping to find optimal character match from the database and evaluate the expression.
\end{list2}

\textbf{GIS Contour Plotting}\\
  \textsl{Guide : Prof. Miling Sohoni and Prof. Adsul Bharat} \hfill \emph{Summer 2012}
\begin{list2}
\item Plotting \textbf{elevation contours} using sample data point from \emph{Google Maps API}.
\item Generated \emph{KML} files and overlaid them on \emph{Google Earth} using \emph{python} scripts. \\
\end{list2}

\textbf{All Terrain Vehicle} \hfill
\textsl{Institute Technical Summer Project} \hfill \emph{Summer 2012} \\ 
Designed and custom manufactured an all terrain bot which could be controlled using serial input and was awarded \textbf{Best Complete Project}

\section{\mysidestyle Interests}

\begin{list2}
\item Active contributor to \textbf{Open Source Projects} with contributions for \emph{Firefox QA} and \emph{Firefox for Android}.
\item Currently developing a programming test bed which can be used as a hosting application for programming contests.\\ \url{http://www.github.com/wncc/prog-test-bed} 
\item Participated in \emph{Yahoo HackU} and created a carpool web application.
\item Created an automatic song tagging application in \emph{Windows 8 Appfest} held in Bengaluru and was the runnerup of the Institute Hackathon conducted by WnCC.
\item Made a Group Expense Manager Android App and a web app for Firefox OS.
\item Frequently go for hiking nearby the institute.
\end{list2}

\section{\mysidestyle Extra \\ Curricular \\ Activities }
\begin{list2}
\item Among the \textbf{Top 20} \emph{Lawn Tennis} players for 2011 batch under the \emph{National Sports Organisation} NSO scheme
\item Performed in \emph{Annual Insync Dance Show}, the biggest dance festival of IITB.
\end{list2}
\section{\mysidestyle Key Courses\\Undertaken}

\textbf{Core:} 
Abstractions and Paradigms in Programming, Computer Architecture*, Database Systems* ,Design and Analysis of Algorithms, Networks*, Automata Theory and Logic, Discrete Structures, Software Systems, Logic Design\\
\textbf{Breadth:} 
Calculus,Economics,Numerical Analysis,Analog Electronics*,Data Analysis and Interpretation,Signals and Systems,Controls and Communications,Linear Algebra and Differential Equations,Introduction to Electric and Electronics Circuits \\
\textbf{Note:} The * marked courses will be completed by November 2013.

\section{\mysidestyle Skills and\\Interests} 
\begin{list2}
\item \textbf{C++}, \textbf{Python}, MIT-\textbf{Scheme}, \LaTeXe, \textbf{Java}, \textbf{Prolog}
\item Operating Systems: Windows, GNU/Linux
\item  Web Development: PHP, HTML, CSS, Js, AJAX
\end{list2}

\end{resume}
\end{document}
