\documentclass[margin,11pt]{resume}
\usepackage{hyperref}
\usepackage{amsmath}
\newcommand{\BigO}[1]{\ensuremath{\operatorname{O}\bigl(#1\bigr)}}
\begin{document}
\begin{resume}

\vspace{25mm}

\section{\mysidestyle Scholastic\\Achievements}

\begin{list2}
\item \textbf{All India Rank 589} in IITJEE 2011 (Top 0.01\%)
\item Achieved an \textbf{All India Rank 36} in ISAT 2011 conducted by Indian Institute of Space Technology (Top 0.03\%)
\item Secured $12^{th}$ position in \textbf{Regional Mathematics Olympiad} conducted by the Dept. of Mathematics \emph{University of Rajasthan} \hfill \emph{2009}
\item Awarded \textbf{AIR 12} for AMTI's \emph{Association of Mathematics Teacher of India} NMTC \emph{National Maths Talent Contest} \hfill \emph{2009}
\item Selected for the following national olympiads: \\
 \textbf{  INPHO} Physics National Top 1 \% \hfill \emph{2010} \\
 \textbf{  INCHO} Chemistry National Top 1 \% \hfill \emph{2010} \\
 \textbf{  INAO} Astronomy National Top 1 \% \hfill \emph{2007,2010} \\
 \textbf{  INMO} Mathematics National Top 1 \% \hfill \emph{2009,2010} \\
\end{list2}
\section{\mysidestyle Research\\Projects\\And\\Internships }

\textbf{Malware Detection in Android} \\
	\textsl{Guide: Prof. Mythili Vukutru} \hfill \emph{Ongoing}
\begin{list2}
\item Implementing a model for static analysis of permissions used by app. 
\item Planning to work on analyzing dynamic behavioral patterns to detect malware.
\end{list2}

\textbf{Web Developer} at \emph{CourseBrew} \hfill \emph{Autumn 2013} 
\begin{list2}
\item Developed a prototype of an online education website. Extensively used \emph{DHTMLx} to create the discussion forum and \emph{dynamic layouts} for the web application.
\end{list2}


\section{\mysidestyle Academic\\Projects}

\textbf{Sequence Alignment on GPU's} \\
\textsl{Guide : Prof. Bernard Menezes} \hfill \emph{Autumn 2013}
\begin{list2}
\item Implemented a version Sequence Alignemnt problem in GPU’s. Used a parallel
Implementation of Needleman-Wunsch algorithm.
\item Tried the Parallel Prefix and Diagonal based apporach to solve the problem. The
approch achieved \BigO{n} complexity as compared to \BigO{n\textsuperscript{2}} in the Serial Version.
\end{list2}


\textbf{Handwriting Calculator} \\
    \textsl{Guide : Prof. Varsha Apte} \hfill \emph{Autumn 2012}
\begin{list2}
\item A\emph{ handwriting based calculator} which identifies and evaluates mathematical expressions written via hand held input.
\item Implemented \textbf{Supervised Machine Learning} based on \emph{feature extraction}. 
\item Used Dynamic Time Warping to find optimal character match from the database and evaluate the expression
\end{list2}

\textbf{TeamFlowy: A Team Management Webapp}\\ \textsl{Guide: Prof. Umesh Bellur} \hfill \emph{Autumn 2013}
\begin{list2}
\item A django based webapp to help manage teams. The webapp supports calendar view of tasks, writing blog posts and setting reminders.
\item Implemented analytics to track team performance using HighCharts Js library. 
\end{list2}

\textbf{Tum Tum Tracker} \hfill Bus Tracking System \hfill
    \url{http://www.tttracker.in}
\begin{list2}
\item Developed the web app using \emph{Google Maps API v3} and asynchronously fetched bus positions and updated them realtime  on the application.
\end{list2}


\textbf{GIS Contour Plotting}\\
  \textsl{Guide : Prof. Milind Sohoni and Prof. Adsul Bharat} \hfill \emph{Summer 2012}
\begin{list2}
\item Plotting \textbf{elevation contours} using sample data point from \emph{Google Maps API}.
\item Used various \emph{kriging} techniques and implemented them efficiently.
\item Generated \emph{KML} files and overlaid them on \emph{Google Earth} using \emph{python} scripts. \\
\end{list2}

\textbf{8-Point FFT on FPGA}\\ \textsl{Guide: Prof. Ashwin Gumasthe} \hfill \emph{Spring 2013}
\begin{list2}
\item Designed and implemented \emph{Fast Fourier Algorithm} on a Field Pro-grammable Gate Array 
\end{list2}



\section{\mysidestyle Positions of\\Responsibility } 


\textbf{Manager} of \emph{The Web and Coding Club} \hfill \emph{2013-2014}\\
WnCC is one of the biggest clubs of IIT Bombay which supports coding and related activities in the institute. Responsibility as a manager includes:
\begin{list2}
\item Conducting workshops, sessions and competitions to improve coding culture among the students and to introduce the community to latest developments in technology, acting as a bridge between the academia and the industry. 
\item Creating awareness about Open Source and encouraging students towards contribution to the same. 
\item Organized major collaborative events in the past which include Yahoo HackU!, Google Appathon (GDG Mumbai), Firefox OS Hackathon (Mozilla India). 
\item Managing student projects and open source initiatives of the club. 
\end{list2}
\textbf{GSA} Google Student Ambassador of IIT Bombay \hfill \emph{2013-2014} \\
\textbf{Convener} of Maths and Physics Club \hfill \emph{2012-2013} \\
\emph{Part of Students Technical Activity Body (STAB), monitoring and mentoring Technical Activities all over the institute}s

\section{\mysidestyle Interests}

\begin{list2}
\item Active contributor to \textbf{Open Source Projects} with contributions for \emph{Firefox QA} and \emph{Firefox for Android} and some other small projects.
\item Developed a hacker news scraper to display top news of the day.
\item Participated in \emph{Yahoo HackU} and created a carpool web application.
\item Created an automatic song tagging application in \emph{Windows 8 Appfest} held in Bengaluru and was the \emph{Runnerup} of the Institute Hackathon conducted by WnCC.
\item Blog about my coding experiences at  \url{http://sushant-hiray.github.io} 
\end{list2}

\section{\mysidestyle Extra \\ Curricular \\ Activities }
\begin{list2}
\item Among the \textbf{Top 20} \emph{Lawn Tennis} players for 2011 batch.
\item Performed in \emph{Annual Insync Dance Show}, the biggest dance festival of IITB.
\end{list2}
\section{\mysidestyle Key Courses\\Undertaken}

\textbf{Core:} 
Abstractions and Paradigms in Programming, Computer Architecture, Compilers*, OS*, AI*, Algorithms in Medical Image Processing*, Database Systems ,Design and Analysis of Algorithms, Networks, Automata Theory and Logic, Discrete Structures, Software Systems, Logic Design\\
\textbf{Breadth:} 
Calculus,Economics,Numerical Analysis,Analog Electronics*,Data Analysis and Interpretation,Signals and Systems,Controls and Communications,Linear Algebra and Differential Equations,Introduction to Electric and Electronics Circuits, Probability and Random Processes* \\
\textbf{Note:} The * marked courses will be completed by April 2014.

\section{\mysidestyle Skills and\\Interests} 
\begin{list2}
\item \textbf{C/C++}, \textbf{Python}, MIT-\textbf{Scheme}, \LaTeXe, \textbf{Java}, \textbf{Prolog}
\item Operating Systems: Windows, GNU/Linux
\item  Web Development: PHP, HTML, CSS, Js, AJAX
\end{list2}

\end{resume}
\end{document}
